Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-03-07 drafts/hybrid_zone.tex
edits

As in \citet{sedghifar2015spatial}, consider where the ancestors of modern-day individuals lived,
i.e., where their lineages fall across geography as we look further back towards the time of first contact.
We say that a locus in a sampled individual is of \emph{ancestry} $A$ if it has been inherited from an individual of species $A$ at the time of secondary contact,
i.e., if its lineage traces back to a spatial position $x<0$.
A block of genome is of ancestry $A$ if every locus in it does the same; 
	this occurs if there is no recombination in this block, or if all lineages generated by recombination events 
	in this block trace back to the $A$ side. 
This process, in which recombination events cause such lineages to \emph{branch},
is illustrated in Figure~\ref{Fig:schematic}.
We say that a block of genome is on the $A$ \emph{background} if it is physically linked to an allele of ancestry $A$ at the selected locus;
if a block of ancestry $A$ includes the selected site then it is necessarily on the $A$ background.
Because the identity of the selected allele determines how selection acts on the haplotype,
and because linked alleles can only move between the $A$ and the $B$ background in heterozygotes, 
a key factor in these models is the density and fecundity of heterozygotes.

%%%%%%%%
\begin{figure}
\includegraphics{figs/BM_schematic}
\caption{
    \textbf{A schematic figure of the lineages along which a segment of genome has been inherited,}
    i.e., showing where the ancestors lived from whom the haplotype was inherited (horizontal axis),
    and how long ago they lived (vertical axis).
    The segment contains the $B$ alelle at the selected locus.
    The black line shows the lineage at the selected site in the sampled individual in the present day (at $\tau=0$).
    The center of the hybrid zone is at geographic position $x=0$; in the region $x>0$, ancestry $A$ is less common,
    and because of negative selection, the selected lineage spends little time there.
    Red dots represent ancestral recombination events that fall in the given segment of genome in an ancestor;
    these can cause the lineage to branch (lineages at linked sites are depicted as colored lines),
    or can switch lineages at linked sites between selected backgrounds 
    (yellow lineages are linked to the $A$ selected locus; blue are linked to $B$).
    Here the initial haplotype is broken up into 3 chunks over 100 generations,
    which switch between selected backgrounds once.
    Based on position of the lineages at $\tau=100$ generations after contact, 
    from left to right the segments are of ancestry $(A,B,B)$.
}\label{Fig:schematic}
\end{figure}

@@

\paragraph{Establishment of the cline at the selected locus}
Deterministic theory predicts that after secondary contact,
the two alleles at the selected locus will form a stable cline \citep{barton1979gene},
affecting neighboring loci as well.
First, we turn our attention to how the cline at the selected locus itself is formed.
Let $p(x,t)$ denote the frequency of the $A$ allele at spatial location $x$ and time $t$.  
Suppose that secondary contact occurred at time $t=0$, 
and that $p(x,0) = 1$ if $x<0$ and $p(x,0)=0$ if $x>0$.
% (In discrete computations, a deme at $x=0$ has $p(0,0)=1/2$.)
Let $\sigma^2$ be the mean squared distance between parent and offspring 
(i.e., the variance of the distribution of dispersal distance).
Assuming that: (i) alleles locally assort into diploids randomly, 
(ii) habitat and dispersal are homogeneous,
(iii) $s$ and $\sigma$ are small, 
and (iv) population density is large,
then the commonly-used equation that $p$ solves is
\begin{align} \label{eqn:cline_pde}
    \dot p = \frac{\sigma^2}{2} \Delta p + s p (1-p) (2p-1) ,
\end{align}
where $\dot p(t,x)$ is the time derivative and $\Delta p$ is the Laplacian,
as in \citet{Bazykin1969}; 
this can be derived as in \citet{Nagylaki1975};
for discussion of diploidy see \citet{christiansen1995genotypic}.
Although there is no known exact analytic solution to this equation, 
the steady-state solution is
$\lim_{t \to \infty} p(x,t) = (1+\tanh(-2x\sqrt{s}/\sigma))/2$ \citep{Bazykin1969}. 
This relies on several approximations, but the general conclusions should be quite robust: 
the stable cline has width of order $\sigma/\sqrt{s}$, and decays exponentially. 
Note that rescaling space and time by $\sigma/\sqrt{s}$ and $1/s$ respectively in equation \eqref{eqn:cline_pde} 
results in a dimensionless equation \citep{Slatkin1973},
implying that the cline establishes over a timescale of the order $1/s$. 
In other words, the cline is established through diffusion, despite being slowed down somewhat by selection against heterozygotes.

@@

\paragraph{Lineages at linked loci}
%YB DID SUBSTANTIAL EDITING OF THIS PARAGRAPH
The behavior of a lineage at a linked locus is similar to a selected locus. 
However, there is one important difference -- in heterozygotes the lineage lineage linked to the selected locus may move between backgrounds. 
Therefore, if we follow back through time a lineage at a locus linked to an $A$ allele, 
it will first tend to be inherited from ancestors to the left (as $A$ lineages drift to the left). 
However, with sufficient time in the hybrid zone, recombination allows this linked locus 
to have been inherited from a $B$-carrying individual,
whose ancestors will tend to be more from the right.

@@

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim}
\caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    with $r=0$ representing the locus under selection. 
    Grey lines represent the same positions from a simulation with
    identical parameters except $s=0$.
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

We expect that, in the absence of selection, blocks of $A$ ancestry across the genome 
will tend to be shorter the further one goes into the $B$ side of the cline,
because they have had more opportunities to recombine with $B$ haplotypes. 
This is seen in Figure \ref{Fig:meanBlockLengthsUnconditioned}.
However, we expect that stretches of $A$ ancestry containing a selected site will be longer
than those that do not contain the selected site at the same spatial location,
because lineages containing the selected site have usually been inherited from the $A$ side of the cline recently. 
As discussed above, we expect these lineages move at speed roughly $\sigma\sqrt{s}$,
so (selected) $A$ alleles at distance $x$ from the cline center
to have last had an ancestor on the $A$ side of the cline around $x/(\sqrt{s}\sigma)$ generations ago 
(compared to $x^2/\sigma^2$ for a neutral allele).
This implies the enclosing $A$ haplotype should be no longer than $\sigma\sqrt{s}/x$.
%\plr{(check predicted decay of mean length $1/x$ in simulations?)}

@@

Genomic regions are inherited from ancestors $T$ generations ago
in blocks of size roughly $1/T$,
so there will be a long segment of $A$ ancestry
if many such adjacent blocks are of the same ancestry.
Ancestries of neighboring blocks are correlated,
due to the branching process described above. 
But, if we assume they are independent, 
then since the block about location $r$ in an individual at geographic location $x$ is of ancestry $A$ with probability $q_A(x,T,r)$,
we'd expect to see, on average, $2q_A(x,T,r)/(1-q_A(x,T,r))$ \alisa{consecutive} blocks of ancestry $A$ about a given site unlinked to the selected site.
This implies the mean length $l(x,m)$ would be $2q_A(x,T,r)/(T(1-q_A(x,T,r)))$,
and the mean conditional length $l_A(x,m)$ would be $2/(T(1-q_A(x,T,r))$.
Furthermore, we know that if $x=0$ or if $T$ is large and $r$ is not too small, that $q_A$ is close to $1/2$;
and for $r<1/T$ that $q_A$ looks like the selected cline.
Also, we know from the discussion above that the lineage of a \emph{selected} $A$ allele,
if it is in the region where $A$ is rare,
moves at speed roughly $\sigma \sqrt{s}$ back towards the $A$ side of the zone,
returning to the region where $A$ is common in about $x/(\sigma \sqrt{s})$ generations.
Therefore, a selected $A$ allele found on the $B$ side of the zone
should carry with it a haplotype of average length $\sigma \sqrt{s}/x$
that looks like haplotypes from the center of the zone.
This analysis suggests that $A$ haplotypes in the center of the zone should be of average length $4/T$ \alisa{should this be $2/T$?};
this is indeed what is seen at distant sites, for instance, in Figure \ref{sfig:blocksAlongChromAncBConditioning_nonnormalized}.
Haplotypes at the selected site are expected to be longer, but still of a length proportional to $1/T$,
suggesting that the normalization in the statistic $C(x,m)$ is appropriate,
as shown in Figure \ref{Supp:adjacentBlocks},
although a numerical prediction of the value of $C(x,m)$ is elusive.

@@

Power will be optimal at intermediate values of $s$.
If selection is too strong, it may be difficult to observe the signal
due to a lack of introgressed selective sites,
while if selection is weak, the selected lineage does not move very fast,
and so the strength of signal from elevated $l_B(m)$ is diminished. 
Indeed, if $s$ is less than $x/(\sigma T)$, then only one block of ancestry $A$ is expected to be seen about a selected $A$ allele,
and $l_A(x,m)$ is expected to be $2/T$.
For similar reasons, power and resolution are best at intermediate $T$.

@@

\begin{figure}
\includegraphics[width=\textwidth]{{figs/results_runid_753324_chr1_start0.48_stop0.52_by0.001_blocksAlongChromNoConditioning_nonnormalized}.pdf}
\caption{
    \textbf{Mean enclosing block length $l(m,x)$}, across the genome (horizontal axis)
    and at different geographic positions (different colored lines).
    Results are from a simulation with 120 demes of 200 diploids each, selection $s=.05$, dispersal $\sigma=3$, 
    and after $T=500$ generations.
}\label{Fig:meanBlockLengthsUnconditioned}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioning}
\caption{
    \textbf{Normalized mean enclosing block length}, $C(m,x)$, after $T=1000$ generations,
    against position relative to the selected locus (horizontal axis)
    located in the center of a 1M chromosome.
    Each line shows the mean block length at that spatial and genomic position
    divided by the mean over the chromosome at that location;
    the simulation was run with $s=1$ and $\sigma=1$,
    50 demes, each containing 500 diploid individuals.
}\label{Fig:blockLengths}
\end{figure}

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioningHighRes}
\caption{Mean block length, $l_B(m)$, along a simulated chromosome of length $1M$ with selected locus of $s=0.01$ at position $0.5M$ in a hybrid zone of $T=1000$. Here each line represents  $l_B(m)$, in a given deme, and is normalized by dividing by mean $l_B(m)$ along the chromosome within the deme. Chromosome were sampled across the hybrid zone, which consists of 50 demes, each containing 500 diploid individuals. This figure represents the same simulation and statistic as Fig.~\ref{Fig:blockLengths}, on a finer genomic scale.
}\label{Fig:blockLengthsZoom}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/number_of_ancestors_tau1000}
\caption{The number of individuals of ancestry $B$ per number of ancestors from secondary contact occurring $T=1000$ generations ago, represented across geographic space. The hybrid zone is 50 demes, each containing 500 diploid individuals.
 Each red or orange line represents a site some distance away (ranging from 0 - 0.01) from the selected site (here $s=0.01$ and $\sigma=1$). Yellow lines are corresponding positions on an unlinked chromosome with no selected loci, and grey lines are corresponding positions in a simulation with no selection.  Bold lines depict the target of selection when present, and corresponding position on chromosomes not harboring any selected sites.}\label{Fig:family_size}
\end{figure}

@@

\yb{remove this? or, what figure?}
Through our simulations we find also that blocks of ancestry that are have crossed the hybrid zone and are closely linked to the selected site without overlapping it (i.e., blocks that are adjacent to the block containing the selected site) are shorter than average for the spatial location. 
An intuitive explanation for this pattern is that loci physically linked to a selected site have recently come from the center of the zone or beyond. 
Compared to other chromosomes in their new geographic location, these migrants will have on average longer $B$ haplotypes at the selected locus, and shorter $A$ haplotypes nearby.

@@

Our assumption of a single selected locus may have greater consequences. Our model is most relevant to scenarios with few targets of selection scattered throughout the genome, and therefore, our predictions may differ significantly from situations in which the density of selected sites is higher. 
Having numerous selected sites within one ancestry block increases the strength of selection, and the relatively short map distances between linked incompatibilities generates a longer unit which is not readily broken up by recombination. Both factors are expected to result in regions that are surrounded by even longer segments of unbroken ancestry, and will impact expectations of genome-wide pattens of clines and block lengths, as well as the resolution to which one could detect targets of selection. 
\yb{provide citation.}

@@

\subsection*{Patterns of divergence}  
A number of studies have described heterogeneous patterns of genetic divergence across the genome. 
Work on these ``islands of divergence'' \citep{turner2005genomic,Nosil2009} and related patterns have been largely descriptive \citep{Cruickshank2014,Noor2009}.
This paper contributes to a model-based understanding of 
how migration and selection influence such patterns across the genome of hybridizing populations. 
Overall, focusing on lengths of ancestry blocks across the genome brings focus to the processes of migration and selection 
rather than high-level summaries that are somewhat abstracted from the evolutionary process.

>>>>

As in \citet{sedghifar2015spatial}, we consider where the ancestors of modern-day individuals lived,
i.e., where their lineages fall across geography as we look further back towards the time of first contact.
We say that a locus in a sampled individual is of \emph{ancestry} $A$ if it has been inherited from an individual of species $A$ at the time of secondary contact,
i.e., if its lineage traces back to a spatial position $x<0$.
A block of genome is of ancestry $A$ if every locus in it does the same; 
	this occurs if there is no recombination in this block, or if all lineages generated by recombination events 
	in this block trace back to the $A$ side. 
This process, in which recombination events cause such lineages to \emph{branch},
is illustrated in Figure~\ref{Fig:schematic}.
We say that a block of genome is on the $A$ \emph{background} if it is physically linked to an allele of ancestry $A$ at the selected locus;
if a block of ancestry $A$ includes the selected site then it is necessarily on the $A$ background.
Because the identity of the selected allele determines how selection acts on the haplotype,
and because linked alleles can only move between the $A$ and the $B$ background in heterozygotes, 
a key factor in these models is the density and fecundity of heterozygotes.

%%%%%%%%
\begin{figure}
\includegraphics{figs/BM_schematic}
\caption{
    \textbf{A schematic figure of the lineages along which a segment of genome has been inherited,}
    i.e., showing where (horizontal axis) and when (vertical axis) the ancestors, from whom the haplotype was inherited, lived.
    The segment contains the $B$ alelle at the selected locus.
    The black line shows the lineage at the selected site in the sampled individual in the present day (at $\tau=0$).
    The center of the hybrid zone is at geographic position $x=0$; in the region $x>0$, ancestry $A$ is less common,
    and because of negative selection, the selected lineage spends little time there.
    Red dots represent ancestral recombination events that fall in the given segment of genome in an ancestor;
    these can cause the lineage to branch (lineages at linked sites are depicted as colored lines),
    or can switch lineages at linked sites between selected backgrounds 
    (yellow lineages are linked to the $A$ selected locus; blue are linked to $B$).
    Here the initial haplotype is broken up into 3 chunks over 100 generations,
    which switch between selected backgrounds once.
    Based on position of the lineages at $\tau=100$ generations after contact, 
    from left to right the segments are of ancestry $(A,B,B)$.
}\label{Fig:schematic}
\end{figure}

@@

\paragraph{Establishment of the cline at the selected locus}
Deterministic theory predicts that after secondary contact,
the two alleles at the selected locus will form a stable cline,
affecting neighboring loci as well \citep{barton1979gene, Barton1986}.
First, we turn our attention to how the cline at the selected locus itself is formed.
Let $p(x,t)$ denote the frequency of the $A$ allele at spatial location $x$ and time $t$.  
Suppose that secondary contact occurred at time $t=0$, 
and that $p(x,0) = 1$ if $x<0$ and $p(x,0)=0$ if $x>0$.
% (In discrete computations, a deme at $x=0$ has $p(0,0)=1/2$.)
Let $\sigma^2$ be the mean squared distance between parent and offspring 
(i.e., the variance of the distribution of dispersal distance).
Assuming that: (i) alleles locally assort into diploids randomly, 
(ii) habitat and dispersal are homogeneous,
(iii) $s$ and $\sigma$ are small, 
and (iv) population density is large,
then the commonly-used equation that $p$ solves is
\begin{align} \label{eqn:cline_pde}
    \dot p = \frac{\sigma^2}{2} \Delta p + s p (1-p) (2p-1) ,
\end{align}
where $\dot p(t,x)$ is the time derivative and $\Delta p$ is the Laplacian,
as in \citet{Bazykin1969}; 
this can be derived as in \citet{Nagylaki1975};
for discussion of diploidy see \citet{christiansen1995genotypic}.
Although there is no known exact analytic solution to this equation, 
the steady-state solution is
$\lim_{t \to \infty} p(x,t) = (1+\tanh(-2x\sqrt{s}/\sigma))/2$ \citep{Bazykin1969}. 
This relies on several approximations, but the general conclusions should be quite robust: 
the stable cline has width of order $\sigma/\sqrt{s}$, and decays exponentially. 
Note that rescaling space and time by $\sigma/\sqrt{s}$ and $1/s$ respectively in equation \eqref{eqn:cline_pde} 
results in a dimensionless equation \citep{Slatkin1973},
implying that the cline establishes over a timescale of the order $1/s$. 
In other words, the cline is established through diffusion, despite being slowed down somewhat by selection against heterozygotes.

@@

\paragraph{Lineages at linked loci}
%YB DID SUBSTANTIAL EDITING OF THIS PARAGRAPH
The behavior of a lineage at a linked locus is similar to a selected locus. 
However, there is one important difference -- in heterozygotes the lineage linked to the selected locus may move between backgrounds. 
Therefore, if we follow back through time a lineage at a locus linked to an $A$ allele, 
it will first tend to be inherited from ancestors to the left (as $A$ lineages drift to the left). 
However, with sufficient time in the hybrid zone, recombination allows this linked locus 
to have been inherited from a $B$-carrying individual,
whose ancestors will tend to be more from the right.

@@

\begin{figure}
\includegraphics{figs/alleleFrequencies_sim}
\caption{
    Frequency of ancestry $B$,
    across geography at different physical positions on the genome, simulated for a hybrid zone
     $T=100$ generations after secondary contact, with $s=0.1$,
     using 50 demes, each with 500 diploid individuals and $\sigma=1$.
    Each line represents a locus some distance $r$ away from the true target of selection, 
    with $r=0$ representing the locus under selection. 
    Grey lines represent the same positions from a simulation with
    identical parameters except that $s=0$.
    Corresponding theoretical quantities are shown juxtaposed in Figure \ref{sfig:alleleFreq_tau100_comparison};
    the same plot is shown with weaker selection in Figure \ref{alleleFreq_tau100_weaker_s} and at a longer time in Figure \ref{alleleFreq_tau1000}.
}\label{alleleFreq_tau100}
\end{figure}

@@

We expect that, in the absence of selection, blocks of $A$ ancestry across the genome 
will tend to be shorter the further one goes into the $B$ side of the cline,
because they have had more opportunities to recombine with $B$ haplotypes. 
This is seen in Figure \ref{Fig:meanBlockLengthsUnconditioned}.
However, we expect that stretches of $A$ ancestry containing a selected site will be longer
than those that do not contain the selected site at the same spatial location,
because lineages containing the selected site have usually been inherited from the $A$ side of the cline recently. 
As discussed above, we expect these lineages move at speed roughly $\sigma\sqrt{s}$,
so (selected) $A$ alleles at distance $x$ from the cline center
to have last had an ancestor on the $A$ side of the cline around $x/(\sigma\sqrt{s})$ generations ago 
(compared to $x^2/\sigma^2$ for a neutral allele).
This implies the enclosing $A$ haplotype should be no longer than $\sigma\sqrt{s}/x$.
%\plr{(check predicted decay of mean length $1/x$ in simulations?)}

@@

Genomic regions are inherited from ancestors $T$ generations ago
in blocks of size roughly $1/T$,
so there will be a long segment of $A$ ancestry
if many such adjacent blocks are of the same ancestry.
Ancestries of neighboring blocks are correlated,
due to the branching process described above. 
But, if we assume they are \emph{independent}, 
then since the block about location $r$ in an individual at geographic location $x$ is of ancestry $A$ with probability $q_A(x,T,r)$,
we would expect to see, on average, $2q_A(x,T,r)/(1-q_A(x,T,r))$ \alisa{consecutive} blocks of ancestry $A$ about a given site unlinked \alisa{unlinked, or linked?} to the selected site.
This implies the mean length $l(x,m)$ would be $2q_A(x,T,r)/(T(1-q_A(x,T,r)))$,
and the mean conditional length $l_A(x,m)$ would be $2/(T(1-q_A(x,T,r))$.
Furthermore, we know that if $x=0$ or if $T$ is large and $r$ is not too small, that $q_A$ is close to $1/2$;
and for $r<1/T$ that $q_A$ looks like the selected cline.
Also, we know from the discussion above that the lineage of a \emph{selected} $A$ allele,
if it is in the region where $A$ is rare,
moves at speed roughly $\sigma \sqrt{s}$ back towards the $A$ side of the zone,
returning to the region where $A$ is common in about $x/(\sigma \sqrt{s})$ generations.
Therefore, a selected $A$ allele found on the $B$ side of the zone
should carry with it a haplotype of average length $\sigma \sqrt{s}/x$
that looks like haplotypes from the center of the zone.
This analysis suggests that $A$ haplotypes in the center of the zone should be of average length $4/T$;
this is indeed what is seen at distant sites, for instance, in Figure \ref{sfig:blocksAlongChromAncBConditioning_nonnormalized}.
Haplotypes at the selected site are expected to be longer, but still of a length proportional to $1/T$,
suggesting that the normalization in the statistic $C(x,m)$ is appropriate,
as shown in Figure \ref{Supp:adjacentBlocks},
although a numerical prediction of the value of $C(x,m)$ is elusive.
\alisa{Above argument assumes independence between lineages. Does this make block lengths conservative? }

@@

Power will be optimal at intermediate values of $s$.
If selection is too strong, it may be difficult to observe the signal
due to a lack of introgressed selected sites,
while if selection is weak, the selected lineage does not move very fast,
and so the strength of signal from elevated $l_B(m)$ is diminished. 
Indeed, if $s$ is less than $x/(\sigma T)$, then only one block of ancestry $A$ is expected to be seen about a selected $A$ allele,
and $l_A(x,m)$ is expected to be $2/T$.
For similar reasons, power and resolution are best at intermediate $T$.

@@

\begin{figure}
\includegraphics{figs/blocksAlongChromAncBConditioningHighRes}
\caption{\textbf{Normalized mean enclosing block length}, $l_B(m)$, along a simulated chromosome of length $1M$ with selected locus of $s=0.01$ at position $0.5M$ in a hybrid zone of $T=1000$. Here each line represents  $l_B(m)$, in a given deme, and is normalized by dividing by mean $l_B(m)$ along the chromosome within the deme. Chromosome were sampled across the hybrid zone, which consists of 50 demes, each containing 500 diploid individuals. This figure represents the same simulation and statistic as Fig.~\ref{Fig:blockLengths}, on a finer genomic scale.
}\label{Fig:blockLengthsZoom}
\end{figure}

@@

\begin{figure}
\includegraphics{figs/number_of_ancestors_tau1000}
\caption{\textbf{Mean family size of haplotypes.} The number of individuals of ancestry $B$ per number of ancestors ($F_B(m,x)$) from secondary contact occurring $T=1000$ generations ago, represented across geographic space. The hybrid zone is 50 demes, each containing 500 diploid individuals.
 Each red or orange line represents a site some distance away (ranging from 0 - 0.01) from the selected site (here $s=0.01$ and $\sigma=1$). Yellow lines are corresponding positions on an unlinked chromosome with no selected loci, and grey lines are corresponding positions in a simulation with no selection.  Bold lines depict the target of selection when present, and corresponding position on chromosomes not harboring any selected sites.}\label{Fig:family_size}
\end{figure}

@@

%\yb{remove this? or, what figure?}
Through our simulations we find also that blocks of ancestry that are have crossed the hybrid zone and are closely linked to the selected site without overlapping it (i.e., blocks that are adjacent to the block containing the selected site) are shorter than average for the spatial location (Figure~\ref{Supp:adjacentBlocks}). 
An intuitive explanation for this pattern is that loci physically linked to a selected site have recently come from the center of the zone or beyond. 
Compared to other chromosomes in their new geographic location, these migrants will have on average longer $B$ haplotypes at the selected locus, and shorter $A$ haplotypes nearby.

@@

Our assumption of a single selected locus may have greater consequences. Our model is most relevant to scenarios with few targets of selection scattered throughout the genome, and therefore, our predictions may differ significantly from situations in which the density of selected sites is higher. 
Having numerous selected sites within one ancestry block increases the strength of selection, and the relatively short map distances between linked incompatibilities generates a longer unit which is not readily broken up by recombination. Both factors are expected to result in regions that are surrounded by even longer segments of unbroken ancestry, and will impact expectations of genome-wide pattens of clines and block lengths, as well as the resolution to which one could detect targets of selection \citep{Slatkin1975b}.

@@

\subsection*{Patterns of divergence}  
A number of studies have described heterogeneous patterns of genetic divergence across the genome. 
Work on these ``islands of divergence'' \citep{turner2005genomic,Nosil2009} and related patterns have been largely descriptive \citep{Cruickshank2014,Noor2009}.
Our study here contributes to a model-based understanding of 
how migration and selection may influence such patterns across the genome of hybridizing populations. 
Overall, focusing on lengths of ancestry blocks across the genome brings focus to the processes of migration and selection 
rather than high-level summaries that are somewhat abstracted from the evolutionary process.
